Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2021-09-28 ch-experiment.tex
Add quantitative analysis to ch4.

@@

\subsection{Network Topologies}
The minimum number of participants required is determined by a number of factors.
First, the long-path pod assignment method results in a minimum number of pods,
determined by the chosen parameters.
Specifically, the pod assignments for each round beyond the first are determined
by a unique prime number,
and the number of pods is a multiple of that prime.
For $T=3$ rounds, two primes are necessary and choosing the lowest two (2, 3)
yields the lowest minimum number of pods: 3.
For all pods to have at least 4 members, the minimum number of participants in
the long-path treatment is 12.

\subsection{Quantifying Preferences, Conflict, and Agreement}

>>>>

\section{Quantitative Analysis}

The primary quantitative data will be the results of the ranked-choice
polls conducted before and after each stage of deliberation.
These results represent individual participants' stated preferences at multiple
time points.
Standard tools from social choice theory can be applied to such rank-ordered
preferences \cite{arrow_social_2012, brandt_computational_2012}.
At each time, these preferences can be aggregated into a {\em preference profile}
representing the collective preferences of all participants in a treatment group.
Preference profiles can be used to aggregate individual preferences into a single
ranking via a {\em social welfare function}.
Similarly, preference profiles can be used to select a single winner via a
{\em social choice function}.
These social choice and social welfare functions represent voting methods.
Different voting methods can potentially yield different results for the same
preference profile.
However, the more similar preferences are across individual participants,
the more likely it is that different voting methods will yield the same winner
or social ranking.
For example, when one proposal beats all others in pairwise contests, it is known as the
{\em Condorcet winner}.
Many voting methods yield the Condorcet winner when it exists, but the existence
of a Condorcet winner is not guaranteed.

For the purposes of this dissertation, the preference profiles will be used
to quantify agreement and conflict over the course of deliberation.
Within social choice theory, agreement can be defined by a {\em consensus class},
a set of preference profiles meeting one of several consensus criteria
\cite{elkind_rationalizations_2016}.
Examples include strong unanimity (of rank orders),
unanimity (of winners),
majority (existence of majority),
Condorcet (existence of Condorcet winner),
and transitivity (of social preference).
On the most restrictive end, in strong unanimity and unanimity,
all decision-makers prefer the same alternative.
In contrast, transitivity only requires that the social preferences induced by
individual preferences are transitive.
Distance-rationalizable voting systems are defined by projecting the preference
profile onto the nearest consensus profile according to a suitable distance.
For example, Dodgson's method \cite{dodgeson_method_1876, brandt_computational_2012}
defines a distance based on swapping adjacent entries in individual preference profiles.
However, for most voting systems,
finding the consensus profile that minimizes distance is NP-Hard
\cite{elkind_rationalizations_2016}.
Social choice theory also provides measures of distances between two individual
preference rankings.
These measures can be extended to create measures of agreement for entire
preference profiles that can be calculated efficiently.

One possibility is to measure the distance from strong unanimity.
Two such methods will be used to analyze the results of the deliberation experiment:
the mean Kendal tau metric and the mean Spearman correlation.
The Kendal tau metric is the number fraction of pairwise contests that have
different results between two profiles \cite{kendall_new_1938}}.
By averaging this measure over all pairs of members, an overall measure of agreement can be calculated for the group.
This measure does not incorporate information about win/loss margins,
only whether an alternative wins or loses.
To quantify the win/loss margin, the mean Spearman correlation will be used.
The Spearman correlation is the linear coefficient of correlation between the
rank orders of alternatives for two voters \cite{spearman_proof_1904}.
As with Kendall tau, the Spearman correlation can be averaged over all pairs of
members to determine a measure of agreement for the entire group.
It must be noted that representing agreement with a single number will inevitably
ignore important information.
Neither of these measures distinguishes a small number of voters disagreeing
on many comparisons from a large number of voters disagreeing on a few.
The Spearman correlation is also unable to distinguish these from situations in
which a small number of voters disagree by a very large margin.

While unanimity might be preferred,
it may sometimes be more realistic to focus on transitivity.
This consensus class requires only that the social preferences between pairs
of alternatives are transitive.
Such preference profiles guarantee that a Condorcet winner will exist,
bringing many different voting methods into agreement on which should win.

The deviation from transitivity will be qunatified by counting the number
of ranked-pair violations.
When performing a vote by the Tideman ranked pair system,
the relative order of two alternatives in the social preference is
determined by the winner of a pairwise vote,
except in the special case that contests with a higher margin have already
constrained their order due to transitivity.
In the latter case, the winner of the pairwise contest may have a lower
position in the social preference.
If this situation occurs, the social preference is intransitive and there may
not be a Condorcet winner.
Each such pair represents a contest violating the social ranking,
so the fraction of such pairs
can be used to quantify the strength of intransitivity in the group’s preferences.
This measure has the property that a Condorcet winner is guaranteed when the value is 0.

\section{Power Analysis}
The minimum number of participants required is determined by a number of factors.
First, the long-path pod assignment method results in a minimum number of pods,
determined by the chosen parameters.
Specifically, the pod assignments for each round beyond the first are determined
by a unique prime number,
and the number of pods is a multiple of that prime.
For $T=3$ rounds, two primes are necessary and choosing the lowest two (2, 3)
yields the lowest minimum number of pods: 3.
For all pods to have at least 4 members, the minimum number of participants in
the long-path treatment is 12.

@@
